\chapter{Introduction}

\textit{The following text is a message to the student and should be removed during the writing process.}

Please note the following instructions regarding an MSc thesis outlined in the study handbook: 

``During the first month, the student is to submit a project plan outlining the objective of the thesis and justification for same to his/her supervisor. In the project plan, the student is also to take into account the overarching learning objectives listed above. When submitting the thesis, the student is to enclose a separate document presenting the original project plan and a revision of same, where appropriate. In addition, the document is to include a brief auto-evaluation of the project process.''

To learn more about the rules for an MSc thesis, please consult the rules for your own MSc programme at \url{http://sdb.dtu.dk}.

\section{Project plan}
We note that the contents of the project plan is also something we would like to see in the introductory chapter of your thesis. In fact, you can reuse your final project plan (possibly extended) as the introduction. If you prefer to write an introduction from scratch, it is, of course, important that it is consistent with the final project plan.

\section{The ``separate document''}
It is also important to note that the separate document containing
\begin{itemize}
\item original project plan
\item possibly revised project plan. 
\item brief self-evaluation
\end{itemize}
mentioned above will be passed on to the external examiner and since it contains the learning goals and the objectives for your thesis, it will be taken into account when your thesis is assessed. 

